---
title: "FAME dataset from London Datastore"
author: "NP"
date: "28/10/2018"
output: 
  html_document:
    number_sections: true
    theme: readable
    self_contained: no
---
<style>
  h1, h2, h3, h4, h5, h6{
    color: #668e81;
    font-family: "arial narrow", helvetica;
  }
  h1, h2{
    font-size: 150%
  }
  h2{
    font-variant: small-caps
  }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Map of london businesses from London Datastore

***
Reference URLs

http://www.sthda.com/english/wiki/computing-and-adding-new-variables-to-a-data-frame-in-r  
https://data.london.gov.uk/dataset/strategic-industrial-location-points-london-plan-consultation-2009  
https://data.london.gov.uk/dataset/strategic-industrial-location-points-london-plan-consolidated-alterations-2004  
https://data.london.gov.uk/dataset/town-centre-locations-2015  
https://data.london.gov.uk/dataset/statistical-gis-boundary-files-london  
https://data.cdrc.ac.uk/dataset/tlrn  
https://data.london.gov.uk/dataset/directory-of-london-businesses  

http://www.siccodesupport.co.uk/  

***

**libraries**
```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(readr)
library(maptools)
library(RColorBrewer)
library(classInt)
#library(OpenStreetMap)
library(sp)
library(rgeos)
library(tmap)
library(tmaptools)
library(sf)
library(rgdal)
library(geojsonio)
library(ggplot2)
library(spData)
library(tidyverse)
```

## prepare dataset

Read from RDS server
```{r, message=FALSE, warning=FALSE}
bil <- read_csv("/Volumes/ritd-ag-project-rd00lq-jamfe87/GIS_Analysis/dataRaw/businesses-in-london.csv")
```

Create variable 'division' from variable 'SICCode.SicText_1' substract chr 1 to 4 (first 4 characters)
```{r, message=FALSE, warning=FALSE}
bil <- mutate(bil, division = substr(SICCode.SicText_1, 1, 4))
```

Change chr to num for 'division' variable
```{r, message=FALSE, warning=FALSE}
bil$division <- as.numeric(as.character(bil$division))
```

Convert numeric to factor to create Division labels 
```{r}
bil$divname <- cut(bil$division, 
                  breaks = c(-Inf, 999, 1499, 1799, 1999, 3999, 4999, 5199, 5999, 6799, 8999, 9729, 9999),
                  labels = c("Agriculture, Forestry and Fishing", "Mining", "Construction", "not used", "Manufacturing","Transportation, Communications, Electric, Gas and Sanitary service", "Wholesale Trade", "Retail Trade", "Finance, Insurance and Real Estate", "Services", "Public Administration", "Nonclassifiable"), right = TRUE)
```

Count number of variables in 'divname'
```{r, message=FALSE, warning=FALSE}
bil$divname <- as.character(bil$divname)
# length(unique(bil[["divname"]])) # [1] 13 - Not necessary, see next results from next function
library(plyr)
library(knitr)
sumt <- count(bil, vars = "divname")
kable(sumt, caption = "Division Frequency")
```

## generate quick map

Convert to dataframe - to SP object - to SF object
```{r}
bildf <-as.data.frame(bil)
```

Get long and lat from your data.frame. Make sure that the order is in lon/lat.
```{r}
latlon <- bildf[,c('long','lat')]
bilsp <- SpatialPointsDataFrame(coords = latlon, data = bil,
                               proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"))
```

SP to SF
```{r}
bilsf <- st_as_sf(bilsp)
```

/Volumes/ritd-ag-project-rd00lq-jamfe87/GIS_Analysis/dataProcessed/

```{r}
st_write(bilsf,"/Volumes/ritd-ag-project-rd00lq-jamfe87/GIS_Analysis/dataProcessed/fame_points_ldn.csv", layer_options = "GEOMETRY=AS_WKT", delete_dsn=TRUE)
```


Subset by 'Manufacturing' . Plotting 'bil' won't work quickly because N = 1,130,474 obs.
```{r}
man <- subset(bilsf, divname == "Manufacturing")
```

Plot quick map "Manufacturing"
```{r}
qtm(man)
```

How many 'classes' of Manufacturing? (see 'Division' number)
```{r}
suMan <- count(man, vars = "division")
```

```{r}
head(man$SICCode.SicText_1)
```

```{r}
head(bilsf$SICCode.SicText_1)
```

Extract all characters before "-"
```{r}
code <- sub("\\-.*", "", man$SICCode.SicText_1)
```

Create variable 'code'
```{r}
man <- mutate(man, code = sub("\\-.*", "", man$SICCode.SicText_1))
```


Style map 'Manufacturing'

```{r fig.height=6, fig.width=8, dpi=300, out.width="2000px"}
tmap_mode("plot") # or "plot" or "view"
fpoint <- tm_shape(man) + 
  tm_symbols(size=0.05,
             shape = 20,
             col = "magenta", 
             alpha = .1,
             border.lwd = NA) +
  tm_layout(inner.margins = c(0.05, 0.05, 0.05, 0.05), frame = F)
fpoint
```

```{r}
tmap_save(fpoint, "/Users/nicolas/Documents/R_Github/pnum/fpoint.png", dpi=600)
```

## interactive map manufacturing

```{r message=FALSE, warning=FALSE}

# tmap_mode("view") # or "plot" or "view"
# tm_shape(man) + 
#   tm_symbols(size=0.001,
#              shape = 20,
#              col = "magenta", 
#              alpha = .1,
#              border.lwd = NA
#   )

```

