---
title: "Interactive Nomis + Openmapping SS"
author: "np"
date: "06/11/2018"
output: 
  html_document:
    number_sections: true
    theme: readable
---
<style>
  h1, h2, h3, h4, h5, h6{
    color: #668e81;
    font-family: "arial narrow", helvetica;
  }
  h1, h2{
    font-size: 150%
  }
  h2{
    font-variant: small-caps
  }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Openmapping space syntax

libraries

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(sf)
library(tmap)
library(maptools)
#library(classint) 
#library(OpenStreetMap)
library(RColorBrewer)
#library(Sp)
library(rgeos)
library(tmap)
library(tmaptools)
#library(downloader)
library(rgdal)
library(geojsonio)
library(leaflet)
```

Reference URLs  

https://www.ons.gov.uk/methodology/geography/ukgeographies/censusgeography  

https://github.com/spacesyntax/OpenMapping  

https://www.r-bloggers.com/5-ways-to-subset-a-data-frame-in-r/  

https://stackoverflow.com/questions/11562656/calculate-the-mean-by-group  

http://zevross.com/blog/2018/10/02/creating-beautiful-demographic-maps-in-r-with-the-tidycensus-and-tmap-packages/  

https://geocompr.robinlovelace.net/adv-map.html

https://rstudio.github.io/leaflet/basemaps.html  

http://leaflet-extras.github.io/leaflet-providers/preview/index.html  

https://rpubs.com/adam_dennett/427207  

http://pro.arcgis.com/en/pro-app/help/mapping/layer-properties/data-classification-methods.htm  

https://github.com/mtennekes/tmap/issues/175  


## prepare data

Read Openmapping data
```{r message=FALSE, warning=FALSE}
#ssx <- read_csv("/Volumes/ucfnnap/R/Rprojects/ssyntax/OpenMapping-gb-v1_csv/csv/ssx_openmapping_gb_v1.csv") # 2,063,322 observations of 36 variables
```

Read Omnis data
```{r message=FALSE, warning=FALSE}
nom <- read_csv("/Volumes/ritd-ag-project-rd00lq-jamfe87/GIS_Analysis/dataProcessed/nomis_4835.csv") # 4,835 obs.
```

Create variable 'lsoa11_cd' from variable 'lsoa11_2011' substract chr 1 to 4 (first 4 characters)
```{r, message=FALSE, warning=FALSE}
nom <- mutate(nom, lsoa11_cd = substr(lsoa_2011, 1, 9))
```

Read lsoa codes for London
```{r, message=FALSE, warning=FALSE}
#lsoa_ldn <- read_csv("/Volumes/ritd-ag-project-rd00lq-jamfe87/GIS_Analysis/dataProcessed/lsoa_ldn.csv") # 4,835 obs.
#class(lsoa_ldn)
```

Covert dataframe column to vector
```{r}
#lsoa_ldnV <- as.vector(lsoa_ldn$lsoa_ldn, mode = 'any')
```

"Subset ssx with London lsoa codes 'lsoa_ldnV'"

Read SSX dataset for london 'ssx_ldn.csv'

```{r}

#ssx_ldn <- ssx[ssx$lsoa11cd %in% lsoa_ldnV,] # 111,582 obs.
#write_csv(ssx_ldn, "/Volumes/ritd-ag-project-rd00lq-jamfe87/GIS_Analysis/dataProcessed/ssx_ldn.csv")
ssx_ldn <- read_csv("/Volumes/ritd-ag-project-rd00lq-jamfe87/GIS_Analysis/dataProcessed/ssx_ldn.csv")
```

Calculate **mean value** for lsoa of choice2kmrank

```{r}
choice2 <- aggregate(choice2kmrank ~ lsoa11cd, ssx_ldn, mean )

```

Load LSOA London boundaries geometries

```{r}
censusb <- read_shape("/Volumes/ucfnnap/made_in_london/GISanalysis/dataRaw/statistical-gis-boundaries-london/ESRI/LSOA_2011_London_gen_MHW.shp")
qtm(censusb)
```

## append choice data
```{r message=FALSE, warning=FALSE}
join1 <- append_data(censusb, choice2, key.shp = "LSOA11CD", key.data = "lsoa11cd", ignore.duplicates = TRUE, ignore.na = TRUE)
```


## append nomis data
```{r message=FALSE, warning=FALSE}
join1 <- append_data(join1, nom, key.shp = "LSOA11CD", key.data = "lsoa11_cd", ignore.duplicates = TRUE, ignore.na = TRUE)
names(join1)
```

## leaflet base map

```{r}
# join1SP <- join1 %>%
#   st_transform(crs = 4326) %>%
#   as("Spatial")
```

```{r}

# pal <-colorBin("PuBuGn", join1SP$Count, n=7)
# 
# leaflet(join1SP) %>%
#   addProviderTiles("Esri.WorldImagery") %>%
#   addPolygons(stroke = FALSE, 
#               fillOpacity = 0.7, 
#               smoothFactor = 0.5,
#               color = ~pal(Count),
#               popup = ~Count)

```

tmap view COUNT
```{r}
tmap_mode("view")

manuCP <- tm_shape(join1) +
  tm_polygons("Count",
              style="jenks",
              palette="PuBuGn",
              alpha = 0.6,
              title="Manufacturing Count. per LSOA",
              border.col = "white",
              lwd=0.5) +
  tm_basemap(server="Esri.WorldImagery")
manuCP
```

tmap two polygons layers
```{r}
manu2 <- tm_shape(join1) +
  tm_polygons(c("Count", "choice2kmrank"),
              style="jenks",
              palette=list("PuBuGn","-RdYlBu"),
              alpha = 0.6,
              title=c("Count","2kmchoice"),
              border.col = "white",
              lwd=0.5) +
  tm_basemap(server="Esri.WorldImagery") +
  tm_facets(as.layers = TRUE)
manu2
```



