---
title: "Nomis + Openmapping SS"
author: "np"
date: "29/10/2018"
output: github_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Openmapping space syntax

libraries

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(sf)
library(tmap)
library(maptools)
#library(classint) 
#library(OpenStreetMap)
library(RColorBrewer)
#library(Sp)
library(rgeos)
library(tmap)
library(tmaptools)
#library(downloader)
library(rgdal)
library(geojsonio)
```

Reference URLs  

https://www.ons.gov.uk/methodology/geography/ukgeographies/censusgeography  

https://github.com/spacesyntax/OpenMapping  

https://www.r-bloggers.com/5-ways-to-subset-a-data-frame-in-r/  

https://stackoverflow.com/questions/11562656/calculate-the-mean-by-group  

http://zevross.com/blog/2018/10/02/creating-beautiful-demographic-maps-in-r-with-the-tidycensus-and-tmap-packages/  

https://geocompr.robinlovelace.net/adv-map.html

## prepare data

Read Openmapping data
```{r message=FALSE, warning=FALSE}
ssx <- read_csv("/Volumes/ucfnnap/R/Rprojects/ssyntax/OpenMapping-gb-v1_csv/csv/ssx_openmapping_gb_v1.csv") # 2,063,322 observations of 36 variables
```

Read Omnis data
```{r message=FALSE, warning=FALSE}
nom <- read_csv("/Volumes/ritd-ag-project-rd00lq-jamfe87/GIS_Analysis/dataProcessed/nomis_4835.csv") # 4,835 obs.
```

Create variable 'lsoa11_cd' from variable 'lsoa11_2011' substract chr 1 to 4 (first 4 characters)
```{r, message=FALSE, warning=FALSE}
nom <- mutate(nom, lsoa11_cd = substr(lsoa_2011, 1, 9))
```

Read lsoa codes for London
```{r, message=FALSE, warning=FALSE}
lsoa_ldn <- read_csv("/Volumes/ritd-ag-project-rd00lq-jamfe87/GIS_Analysis/dataProcessed/lsoa_ldn.csv") # 4,835 obs.
class(lsoa_ldn)
```

Covert dataframe column to vector
```{r}
lsoa_ldnV <- as.vector(lsoa_ldn$lsoa_ldn, mode = 'any')
lsoa_ldnV
```

Subset ssx with London lsoa codes 'lsoa_ldnV'

```{r}
ssx_ldn <- ssx[ssx$lsoa11cd %in% lsoa_ldnV,] # 111,582 obs.
```

Calculate mean value for lsoa of choice2kmrank

```{r}
choice2 <- aggregate(choice2kmrank ~ lsoa11cd, ssx_ldn, mean )

```

Load LSOA London boundaries geometries

```{r}
censusb <- read_shape("/Volumes/ucfnnap/made_in_london/GISanalysis/dataRaw/statistical-gis-boundaries-london/ESRI/LSOA_2011_London_gen_MHW.shp")
qtm(censusb)
```

## append choice data
```{r message=FALSE, warning=FALSE}
join1 <- append_data(censusb, choice2, key.shp = "LSOA11CD", key.data = "lsoa11cd", ignore.duplicates = TRUE, ignore.na = TRUE)
```

## quick map
```{r}
qtm(join1,fill="choice2kmrank")
```
  
## customize choice map
```{r echo=FALSE, fig.height=6, fig.width=9, message=FALSE, warning=FALSE, dpi=300, out.width="2000px"}
ch <- tm_shape(join1) + 
  tm_polygons("choice2kmrank",
              style="jenks",
              n=7,
              palette="-Spectral",
              title="Choice 2km Mean \nper LSOA",
              border.col="white",
              border.alpha = 0.5,
              lwd = 0.1) +
  tm_layout(inner.margins = c(0, 0, 0, 0.1), frame = F) # b, l, t, r
ch 
```

```{r}
# tmap_save(mH.i, "mH.html")
tmap_save(ch, "ch.png", dpi=600)
```

## append nomis data
```{r message=FALSE, warning=FALSE}
join1 <- append_data(join1, nom, key.shp = "LSOA11CD", key.data = "lsoa11_cd", ignore.duplicates = TRUE, ignore.na = TRUE)
names(join1)
```

## customize nomis data map

```{r}
manu <- tm_shape(join1) +
  tm_polygons("Industry percentage",
              style="jenks",
              palette="PuRd",
              title="Manufacturing perc. per LSOA",
              border.col="white",
              border.alpha = 0.1) +
  tm_layout(inner.margins = c(0, 0.1, 0.05, 0.2), frame = F) # b, l, t, r
manu
```

## Combine maps

```{r}
tmap_mode("plot")
tmap_arrange(ch, manu)
```
```{r}
tmap_mode("view")
# tmap_arrange(ch, manu)

```

## two polygons

```{r}
int <- tm_shape(join1) +
  tm_polygons(c("Industry percentage","choice2kmrank"))
int
```

## via facets
```{r}
# facets = c("Industry percentage","choice2kmrank")
# tm_shape(join1) +
#   tm_polygons(facets) +
#   tm_facets(nrow=1, sync = TRUE)
```


