---
title: "London Manufacturing Profiler"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    number_sections: yes
  html_notebook:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: no
    self_contained: no
---
<style>
* {
  font-family: "Palatino"
}

h1{
    font-size: 190%
}

h2{
    font-size: 160%
}

h3{
    font-size: 150%
}

h4{
    font-size: 130%
}

h5{
    font-size: 110%
}

h6{
    font-size: 90%
}
</style>

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(maptools)
library(RColorBrewer)
library(classInt)
library(sp)
library(rgeos)
library(tmap)
library(tmaptools)
library(sf)
library(rgdal)
library(geojsonio)
library(ggplot2)
library(spData)
library(tidyverse)
library(ggmap)
library(htmlTable)
```

# Introduction

Interactive map development that combines Space Synatax measures and Manufacturing indicators in London

## Data Layers
The following is a selection of data layers to create maps for a graphical investigation of Manufacturing in London.

### a. Space Syntax Measures (OpenMapping)
https://spacesyntax-openmapping.netlify.com/

| | 2 km |10 km |
|:---|---|---|
| Choice | Higher 20% | Higher 20% |
| Integration| Higher 20% | Higher 20% |

### b. Manufacturing/Industrial Measures
https://npalomin.github.io/pnum/LW/LW.html 

1. Industrial Designation Land
2. Manufacturing Jobs per LSOA
3. Directory of London Businesses (POINT data)

##  Maps functionalities

- Data layer selection
- Navigational interactivity (pan and zoom)

# Analysis

## Data collection

Space Syntax
```{r include=FALSE}
LMPs <- read_csv("/Volumes/ucfnnap/R/Rprojects/ssyntax/ldnssx_wkt.csv")
```

```{r}
LMPs <- st_as_sf(LMPs, wkt='WKT', crs=27700)
```

```{r}
fivenum(LMPs$choice2km)
```

```{r}
summary(LMPs$choice10km)
```
```{r}
choice2_20 <-head(LMPs[order(LMPs$choice2km,decreasing=T),],.20*nrow(LMPs))
choice10_20 <-head(LMPs[order(LMPs$choice10km,decreasing=T),],.20*nrow(LMPs))
integration2_20 <-head(LMPs[order(LMPs$integration2km ,decreasing=T),],.20*nrow(LMPs))
integration10_20 <-head(LMPs[order(LMPs$integration10km ,decreasing=T),],.20*nrow(LMPs))
```

Summary tables
```{r}
t1 <- summary(choice2_20$choice2km)
t2 <- summary(choice10_20$choice10km)
t3 <- summary(integration2_20$integration2km)
t4 <- summary(integration10_20$integration10km)
```

```{r}
t1234 <- rbind(t1,t2,t3,t4)
htmlTable(txtRound(t1234, 1), align='r', col.columns = c('none', '#F7F7F7'), css.cell='padding:1em', rnames = c("Choice 2km", "Choice 10km", "Integration 2km", "Integration 10km"), caption="Summary of highest 20% values of Choice and Integration (n=23409)")
```

```{r}
m1 <- qtm(choice2_20) + tm_legend(main.title ="Choice 2km", main.title.size=1, fontfamily='Palatino') + tm_layout(frame=F, main.title.position = "center")
m2 <- qtm(choice10_20) + tm_legend(main.title ="Choice 10km", main.title.size=1, fontfamily='Palatino') + tm_layout(frame=F, main.title.position = "center")
m3 <- qtm(integration2_20) + tm_legend(main.title ="Integration 2km", main.title.size=1, fontfamily='Palatino') + tm_layout(frame=F, main.title.position = "center")
m4 <- qtm(integration10_20) + tm_legend(main.title ="Integration 10km", main.title.size=1, fontfamily='Palatino') + tm_layout(frame=F, main.title.position = "center")
```

```{r}
tmap_arrange(m1, m2, m3, m4, ncol = 2)
```

Read London Business Directory point data
```{r}
points <- read_csv("/Volumes/ritd-ag-project-rd00lq-jamfe87/GIS_Analysis/dataProcessed/fame_points_ldn.csv")
```

```{r}
points <- st_as_sf(points, wkt='WKT', crs=27700)
```

```{r}
man <- subset(points, divname == "Manufacturing")
```

```{r}
qtm(man)
```

Mapdeck-gl
```{r}
devtools::install_github("SymbolixAU/colourvalues", force = TRUE)
devtools::install_github("SymbolixAU/spatialwidget", force = TRUE)
devtools::install_github("SymbolixAU/mapdeck")
```

```{r}
library(mapdeck)
key <- "pk.eyJ1IjoibnBhbG9taW4iLCJhIjoiY2owMDF5YXQxMDA2eDMybmwwd2tqYTU3bSJ9.Icvrku6Q57o8L0gncJI89g"
```

```{r}
mapdeck(token = key, style = mapdeck_style('light')) %>%
  add_scatterplot(man, radius = 50, fill_opacity=100) 
```

```{r}
l_deck <- mapdeck(token = key, style = mapdeck_style('light')) %>%
  add_path(choice10_20)
```

```{r}
library(htmltools)
save_html(l_deck, "l_deck.html")
```



```{r}
library(leaflet)
```

```{r}
leaflet(man) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircles()
```

```{r}
choice10_20
```


```{r}
leaflet(choice10_20) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolylines()
```

# Conclusion

# References

# Bibliography
